---
title: "final_code"
author: "Team-Cheese_Slicer_-_Chopsticks"
date: "12/12/2017"
output: pdf_document
---

```{r setup, include=FALSE warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(dplyr)
library(magrittr)
library(stringr)
library(purrr)
library(geosphere)
library(shiny)
library(leaflet)
```

#Get website

```{r eval=FALSE}
base_url0 = "https://www.apartmentratings.com"

base_url1 = "https://www.apartmentratings.com/nc/durham/"
base_url2 = "https://www.apartmentratings.com/nc/durham/page=1/"
base_url3 = "https://www.apartmentratings.com/nc/durham/page=2/"
base_url4 = "https://www.apartmentratings.com/nc/durham/page=3/"
base_url5 = "https://www.apartmentratings.com/nc/durham/page=4/"
base_url6 = "https://www.apartmentratings.com/nc/durham/page=5/"
base_url = c(base_url1, base_url2, base_url3,
             base_url4, base_url5, base_url6)

apt_url = c()

for (i in 1:6) {
  apt_url0 = base_url[i] %>% read_html() %>%
    html_nodes('a[class="communityLink"]') %>% html_attr("href")
  apt_url = c(apt_url, apt_url0)
}

urls = apt_url %>% unlist() %>% unique() %>% paste0(base_url0, .)
urls = urls[-which(urls %in% "")]
save(urls, file="urls.Rdata")
```

All of our data are from the website https://www.apartmentratings.com/nc/durham/. Firstly we have to get the urls of all 145 apartments, then we scrap the data we need from each of them.   
Since there are no APIs provided by this site, the first thought is to use `rvest` to obtain those ulrs by extracting certain html nodes. But we are banned after the first try, so we use `httrack` to create the mirror website. However, _apartmentratings_ has such an invincible protection mechanism that web copying turns out to be impossible as well. So we download its source code as a tex file and use regular expression to obtain target urls.   
We get banned again when downloading each page from its url using `utils::download.file()`, so we have to download them manually. For each downloaded `.htm` file, we basically use `rvest` and regular expression to extract and categorize the data including `apartment names`, `floor plans`, `distance`, so on and so forth. Finally, we save these data as a dataframe and use it as our sample data for the next part.

#Scraping

```{r eval=FALSE}
#for test only
#site = "webURLs/web24.htm"

#create function for scraping for all 145 websites
apartment_finder = function(site) {

                   #create another small function to extract test from html
                    extract_info = function(node) {
                      site %>% 
                        read_html() %>% 
                        html_node(node) %>% 
                        html_text()
                    }


#count and average score for each individual review
review_score = extract_info('script[type="application/ld+json"]') %>% 
  str_match_all('ratingValue":\\s.(\\d)"')%>% 
  .[[1]]%>% # we know that it will only return one list from each page
  .[,2]%>% # second column is the part inside bracket we need
  as.numeric()

#lon and lat for apartment site
lon_lat = site %>%
  read_html() %>%
  html_text() %>% 
  str_extract_all("\\[\\'longitude\\'\\] = '-\\d+\\.\\d+|\\[\\'latitude\\'\\] = '\\d+\\.\\d+") %>%  
  str_extract_all("-?\\d+\\.\\d+") %>% 
  unlist() %>% 
  as.numeric() %>% 
  t()
#if this information is not complete, either miss longitude or latitude, we treat them as NA for both
if(length(lon_lat) != 2) lon_lat = rep(NA,2)


#apartment name
apt_name = extract_info('.last span')

#floor plan aviable in this apartment
floor_plan = site %>%
  read_html() %>%
  html_nodes('h3[class="link1"]') %>% 
  html_text()

#rent for each floor plan
rent.raw = site %>%
  read_html() %>%
  html_nodes('#floorplans .widget') %>% 
  html_text()
  
#if differnt sizes of room for each floor plan, calculate the average rent for each floor plan
split_rent = unlist(str_split(rent.raw, "Bathroom"), recursive = FALSE) %>% 
  .[str_detect(.,"Price")]

num_rent = unlist(lapply(split_rent,
                          function(i) str_extract_all(str_replace_all(i, ",", ""), "\\$\\d{3,}")),
                   recursive = FALSE) %>% 
  lapply(., function(i) str_replace_all(i, "\\$", ""))

rent_mean = unlist(lapply(num_rent, function(i) mean(as.numeric(i)))) %>% 
  .[!is.nan(.)]

#the length of floor plan and rent not the same, we treat them as NA
#since information is not complete
if(length(rent_mean) != length(floor_plan)) {
  rent = rep(NA, length(floor_plan))
} else {
  rent = rent_mean
}



#extract url first image aviable on apartment rating website(could be NA) 
image_url = site %>%
  read_html() %>%
  html_nodes('.gallery-image') %>% 
  html_attrs() %>% 
  unlist() %>% 
  str_extract("^/.*g$") %>% 
  .[!is.na(.)] %>% 
#only need the first image
  .[1] %>% 
  paste0("http:", .)

if(str_detect(image_url, "A$")) image_url = NA

#distance to chapel(Duke University) unit is meter by default
chapel = c(-78.9424706, 36.0018988)
#since the result return as a 1*1 matrix, we call it by [1]
distance = round(distm(lon_lat, chapel, fun = distHaversine)[1]) %>% 
  as.numeric()

#oringally look for the information for size for each floor plan (sq^2)
#but since this information is not avaible for many apartment
#decide to abandon this process
                          
# #calculate average floor size
# floor = site %>%
#   read_html() %>%
#   html_nodes('#floorplans .widget') %>% 
#   html_text()
# 
# split_floor = unlist(str_split(floor, "\\d Bathroom"), recursive = FALSE)
# 
# num_floor = unlist(lapply(split_floor,
#                           function(i) str_extract_all(str_replace_all(i, ",", ""), "\\.\\d{3,}")),
#                    recursive = FALSE) %>% 
#   lapply(., function(i) str_replace_all(i, "\\.", ""))
# 
# floor_mean = unlist(lapply(num_floor, function(i) mean(as.numeric(i)))) %>% 
#   .[!is.na(.)]
#   
# 
# if(length(floor_mean) != length(floor_plan)) {
#  floor_mean_clean = rep(NA, length(floor_plan))
# } else {
#   floor_mean_clean = floor_mean
# }

#combine all the information as list
info_list = list(apt_name, distance, rent, review_score,floor_plan)#, floor_mean_clean, floor_plan, floor,)

#use if statement to filter out NA info, like some zero length vector or NA element 
if(any(lengths(info_list) == 0 | sapply(info_list, function(i) any(is.na(i))))|length(review_score)==0) {
  df.final = NA
} else {

#generate final dataframe
df.final =  as.data.frame(cbind(apt_name, image_url), 
                          stringsAsFactors = FALSE) %>% 
  slice(rep(1:n(), length(floor_plan))) %>% 
  slice(rep(1:n(),length(review_score)))%>%
  cbind( rent, floor_plan,
        #floor_mean_clean,
        review_score, distance, lon_lat)

colnames(df.final) = c("name", "image", "rent","plan",
                       #"size", 
                       "review","distance", "lon", "lat")
}

# different score

# dif_score = site %>%
#   read_html() %>%
#   html_nodes('#content_PropertyBreakdown .score') %>% 
#   html_text() 

return(df.final)
}

#loading data for web getting process
load("urls.Rdata")
apt.df = data.frame()

for (i in seq_len(133)) {
  df = apartment_finder(paste0("webURLs/web", i, ".htm"))
  if(!is.na(df)){
    apt.df = rbind(apt.df,cbind(df,urls[i]))
  }
}

test.df = apt.df %>% 
  select(-image)

#again filter out the observation with NA inside except the image column
df.complete = apt.df[!rowSums(is.na(test.df)) > 0,]

save(df.complete, file="df_complete.Rdata")
```

Our goals is to extract the name, image url, rent, individual rating/review, floor_plan, longtitude, latitude, company url for each 145 apartment in Durham based on the data from apartmentratings.com



#modeling

```{r eval=FALSE}
load("df_complete.Rdata")
plans = unique(df.complete$plan)
library(R2jags)
get_df = function(pl){
  df = df.complete%>%filter(plan == pl)

  
  cat("data{
      for(i.aprt in 1:n.aprt){ # this i.aprt represents the number of apartments
      C0[i.aprt,1] ~ dnorm(0,0.1)
      C0[i.aprt,2] ~ dnorm(0,0.1)
      C0[i.aprt,3] ~ dnorm(0,0.1)
      C0[i.aprt,4] ~ dnorm(0,0.1)
      C0[i.aprt,5] ~ dnorm(0,0.1)
      }
      }model{
      # likelihood
      for(i in 1:n){# This i represents # of reviews for all individuals
      Y[i] ~ dcat(P[i,])
      # probability of taking a value in one of the categories
      # separated by 5 cuts (we have six ordered categories 0 to 5 star)
      # so P[i,]: dim 1*6
      P[i,1] <- max(min(1 - Q[i,1],1),0)
      for (i.cut in 2:n.cut){
      P[i,i.cut] <- Q[i,i.cut-1] - Q[i,i.cut]
      }
      P[i,n.cut+1] <- max(min(Q[i,n.cut],1),0)
      # random effect
      for(i.cut in 1:n.cut){ # Z[i,]: dim 1*5
      logit(Q[i,i.cut]) <- Z[i,i.cut]
      Z[i,i.cut] <- b1*distance[i] + b2*rent[i] - C[(aprt[i]),i.cut] 
      }
      }
      # priors
      b1 ~ dnorm(0.0,0.01)
      b2 ~ dnorm(0,0.01)
      for(i.aprt in 1:n.aprt){ # C[i.aprt,] : dim 1*5
      C[i.aprt,1:5] <- sort(C0[i.aprt,])
      }
      }", fill=TRUE, file="reorderedlogit.txt")
  #unload.module("glm")
  jags_data = list(Y =as.numeric(df$review)+1, distance =as.numeric(scale(df$distance)),
                   rent = as.numeric(scale(df$rent)),n.cut = (length(unique(df$review))-1), 
                   n = nrow(df),n.aprt = length(unique(df$name)), aprt = as.numeric(as.factor(df$name)))
  
  params = c("P","b1","b2","C")
  
  ni = 50000; nb = 10000; nt = 20; nc = 3
  
  outj = jags(jags_data,parameters=params, model.file="reorderedlogit.txt", 
              n.thin=nt, n.chains=nc, n.burnin=nb, n.iter=ni)
  
  label_prob = outj$BUGSoutput$sims.matrix[,grepl("P",colnames(outj$BUGSoutput$sims.matrix))]

  classprb = lapply(0:5,function(i) label_prob[,cumsum(table(factor(df$name, levels=unique(df$name))))+nrow(df)*i])
  for (i in seq_along(classprb)){
    colnames(classprb[[i]])  = unique(df$name)
  }
  save(classprb, file=paste0("classprb",gsub(" ","",pl),".Rdata"))
}
sapply(plans,get_df)
```

This part is the implementation of random effect ordered logitsic regression with jags. It will take several hours to run which is the reason why we don't run the code every time in the shiny. This is justifiable since we do model every housings in Durham (which has all the data we need for modeling such as floor plan, rent etc.) so unless the user is interested in an apartment with few reviews which the result might change considerably if a new review is posted (it's still an hierarchical model with same value of coefficients between groups so it shouldn't change much anyway), this app should work fine without running the model every time.

The model itself is a modification of a similar model from <a href="http://yusung.blogspot.com/2008/03/ordered-logistic-model-with-varying.html"> this blog post </a> which is written in BUGS. There were some notable differences in BUGS and JAGS such as the treatment of the truncation and prior ordering, so we moved the part where we defined five prior intercepts (we have categories from 0 to 5 stars so we need 5 splits) to the data section and then sorted the intercept values so that each categories are given ordered random intercepts (for this, we followed the prior ordering section in p.36 on JAGS Version 3.4.0 user manual).

The general discription of this model is that we are taking reviews of each individual from each apartment as a realization of a categorical distribution with a certain probabilities for each class (0 to 5 stars) which can be represented as a subtraction of log odds. Furthermore we assume that the log odds are represented by a linear equation with rent and distance from the Duke (which is kind of weird since it's not just Duke people that rent the apartment in Durham but the biggest employer in this area is Duke so we might be able to justify it). Then we also assume that coefficients are the same for all  apartments (the rent and distance is all group variables of each apartment so no individual level predictors are present in this model) and the only difference is in the intercepts which is given an ordered normal distribution as a prior.

The dataframe we get from running this chunk is the MCMC samples of posterior class probabilities for each apartment. We use the weighted average (so 0 to 5 stars will be weighted according to its probability) of this as a score to rank apartments. Since we will get a distribution of this probability our resulting scores will also be a distribution which we cannot compare directly but can be made into a ranking by taking a certain quantile from it and sort accordingly which is what the shiny app does internally given the data form this chunk.

#shiny


```{r}
load("df_complete.Rdata")

#change column name for easier future use
colnames(df.complete)[grepl("url",colnames(df.complete))] = "purl"

#if image is NA, change to another link instead
df.complete$image = df.complete$image %>%ifelse(is.na(.),"https://www.internetbrands.com/wp-content/uploads/2014/05/hometravel_aptrating_2x.png"
                                                ,.)
#calculating how many people can accomodate in each floor plan
#based on numbers of bedrooms
per_room = df.complete$plan %>% 
  gsub("Studio", "1 Bedrooms", .) %>% 
  str_extract_all("\\d Bedrooms") %>% 
  unlist() %>% 
  str_extract_all("\\d") %>% 
  unlist() %>% 
  as.numeric()

#calculating unit rent by dividing total rent by number of people
df.complete$rent = df.complete$rent / per_room

#change distance unit from m to km
df.complete$distance = df.complete$distance/ 1000

#create vector variable contains info for each floor plan
plan_list = list.files(path = ".", pattern = "class.*\\.Rdata", all.files = FALSE,
                       full.names = FALSE, recursive = FALSE,
                       ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE) %>% 
  str_extract( "\\dBedrooms,\\dBathroom(s)?|Studio,\\dBathroom")

#create variable for future use, shiny initiation
first = 0

#https://github.com/rstudio/shiny-examples/tree/master/063-superzip-example
#Many thanks to this superzip example to help us construct the barebones of our shiny app
shinyApp(
  ui <-bootstrapPage(
    
    mainPanel(
      div(class="outer",
          tags$style(
            # Include our custom CSS
            includeCSS("styles.css"),
            includeScript("gomap.js")
          ),
          
         
          leafletOutput("map", width="100%", height="100%"),
          
          #set up of the panel
          absolutePanel(id = "controls", class = "panel panel-default", fixed = TRUE,
                        draggable = TRUE, top = 3, left = "auto", right = 20, bottom = "auto",
                        width = 330, height = "auto",
           #add logo of duke and center             
          tags$img(src = "https://upload.wikimedia.org/wikipedia/commons/thumb/e/e6/Duke_University_logo.svg/1280px-Duke_University_logo.svg.png", 
                   width = "250px", height = "100px",
                   style="display: block; margin-left: auto; margin-right: auto;"),
                        
          h1("Apt Rankings", 
             style = "font-family: 'Lobster', cursive;
             font-weight: 500; line-height: 1.1;", align = "center" 
          ),
                        h4("Top5-Top15"),
                        radioButtons("top",NULL, 
                                     choices = c("5" ,"10","15"),
                                     selected = "5"),
                        h4("Price Range"),
                        selectInput("price", "Below", 
                                    choices = c(550,600, 650, 700, 800,
                                                "Above 800"), selected = "700"),
                        h4("Distance"),
                        selectInput("distance", label="Below", 
                                    choices = c(2*1:4, "Above 10"), selected = "8"),
                        h4("Floor_plan"),
                        selectInput("var", "Below", choices = plan_list, 
                                    selected = "1 Bedrooms, 1 Bathroom"),
                        h4("Uncertianty"),
                        sliderInput("uncertainty",label=NULL, min=0.1, max=0.75, 
                                    value=0.25, step=0.1)
                        
          ),
          #credit for apartmentratings.com for allow us to use their data
          tags$div(id="cite",
                   'Data compiled for ', tags$em('Coming Apart: Copyright © 2017 Apartmentratings.com')
          )
      )
    ),
    
    conditionalPanel("false", icon("crosshair"))
  ),
  
  
  server <- function(input, output, session) {
    
    #create map
    output$map <- renderLeaflet({
      leaflet() %>%
        addTiles() %>%
        setView(lng = -78.8986, lat = 35.9940, zoom = 13) #-78.8986 35.9940 center location of Durham
    })
    
    #create observe for each change in input update markers below
    observe({
      
      new_df = reactive({
        #below code for test purpose only
        # input = data.frame(var="1Bedrooms,1Bathroom",uncertainty = 0.3,price = 900,distance=10000,top = 5)
        price = input$price
        dist = input$distance
       #specify the ending value
        if(dist == "Above 10") dist = 30
        if(price == "Above 800") price = 2000
       
        #change floor_plan notation
        floor_plan = gsub("(\\d)(\\w)","\\1 \\2",input$var) %>% 
          gsub(",", ", ", .)
        
        #create or filter large dataframe
        df = get(load(paste0("classprb",input$var,".Rdata")))
        rm(classprb)
        samps = sapply(df,function(x) apply(x,2,function(i) quantile(i,input$uncertainty)))
        weighted_mean = apply(samps,1,function(x) weighted.mean(0:5,x))
        weighted_mean = data.frame(name = names(weighted_mean),val = weighted_mean,plan = floor_plan)
        return_df = merge(weighted_mean,df.complete,by = c("name","plan"))
        return_df = return_df%>%
          filter(!duplicated(name))%>%
          filter(rent< as.numeric(price))%>%
          filter(distance< as.numeric(dist))%>%
          arrange(desc(val))%>%
          slice(1:as.numeric(input$top))
     
        return_df
      })
      
      #filter a even small dataframe baseon the movement of map
      #special thanks to superzip expamle again
      small_df = reactive({
        if (is.null(input$map_bounds))
          return(new_df()[FALSE,])
        bounds <- input$map_bounds
        latRng <- range(bounds$north, bounds$south)
        lngRng <- range(bounds$east, bounds$west)
        
        subset(new_df(),
               lat >= latRng[1] & lat <= latRng[2] &
                 lon >= lngRng[1] & lon <= lngRng[2])
        
      })
      #print(nrow(small_df()))(test only)
    
    #if the above dataframe have zero row(empty dataframe) should give warning to user
    #could be 1.harsh input 2.no observation within the map they are looking at
    if(nrow(small_df()) == 0) {
      #since everytime we open the map, it gives us the warning, we assume by default the dataframe above
      #will have zero row no matter what, so we decide one more condition, if it is the second time have
      #zero row, we then have the warning instead
      if(first ==0){
       #update global value, so it is not 0 instead  
        first<<-1
        }else{
         #show model dialog with the warning message 
         showModal(modalDialog(
            title = HTML('<center><font color="red">Warning: No results found for this input</font></center>'),
            HTML("<center><img src=https://i.imgur.com/nmpYQx2.jpg height = '400', width = '300'></center>"),
            easyClose = TRUE,footer = NULL
          ))}
      }
      
     #create custom color for markers below(only allowed color can not use rcolorbrewer 
      col_var = c('red', 'white', 'lightblue', 'orange', 'green', 'beige', 
                  'lightgreen', 'blue',  'lightred', 'purple',  'pink',
                  'cadetblue',  'darkred','gray', 'lightgray')
      
      #create markers with different colors and rankings(number)
      icons <- awesomeIcons(
        icon = 'ios-close',
        iconColor = 'black',
        library = 'ion',
        fontFamily = "system-ui",
        text = 1:input$top,
        markerColor = col_var[1:input$top]
      )
      
      #info with apartment name, floor plan and rent as well as image on the pop up of the marker when clicked
      content <- paste0(
        "<b><a href=",small_df()$purl,' target="_blank">',small_df()$name,"</a></b><br/>",
        "Floor_plan: ",small_df()$plan,"<br/>",
        "Rent: ",round(small_df()$rent),"<br/>",
        "<img src=", small_df()$image, " height = '200', width = '200'>")
      
      
      #update the markers each time when we change input or move/zoom the map
      leafletProxy("map") %>%
        clearMarkers() %>%
        addAwesomeMarkers(
          small_df()$lon, small_df()$lat, icon=icons,
          popup = content)
    })
    
  })
#special thanks to my teammate at the end for allowing me to use leaflet in this assigment and help me debug      
```

Shiny in the server:
https://victor9496.shinyapps.io/apt_rating/

For our shiny app, we follow the example from shiny website <a href="https://github.com/rstudio/shiny-examples/tree/master/063-superzip-example"> superzip </a>.

we require users to provide the following inputs:

1. Numbers of ranking(top 5, 10,15)

2. Unit price(the range below specified average price:total rent / number of bedroom)

3. Distance(distance(km) from apartment to Duke University (Chapel) )

4. Floor plan(Studio, One Bedroom, etc.)

5. Uncertainty(which point we take from posterior distribution)

In terms of output,  markers will show up in the map with different colors and rankings for the apartment that stand out from the user inputs above, the markers also contain pop-up that includes name of apartment(w/ hyper-link), rent, floor_plan and the picture(if available).

If there is no ranking/observation based on the combination of the user input, we will provide a "warning message" to advise users to change their input.

Moreover, our ranking is also based on boundary of the map user in at the time, depending on the user behvaior (zoom in/out, move around  the map), the rankings will be constantly updated each time; therefore, if user decide to browsing the map outside Durham area or zoom in too much with no data(apartment) availble in that area, it will show the "warning message" as above.

